{ \centering Scientific Report - Summary of Research\\ ~\\ Automatized compilation of sequential software to a diverse set of hardware accelerators\\ } ~\\ \vspace{18em} \large Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
WIP

The focus of year three in this Ambizione project was move our polyhedral core
infrastructure into real-world compilers (e.g, LLVM/MLIR) and improve its
performance and scalability. In addition, we worked on establishing backends
for targetting accelerators such as GPUs and FPGAs. Finally, we worked on
performance modelling. As mentioned in the year 2 report, our focus moved from
Julia to MLIR as a compiler and programming language infrastructure.

@@

\begin{enumerate}
\item Fast, robust, and correct polyhedral libraries
\item Solid polyhedral compiler infrastructure
\begin{itemize}
\item  Modular pattern-based optimizations for CPU and GPU systems
\item 
DeLICM: Scalar dependence removal
\end{itemize}
\item Domain-specific optimization for climate science
\end{enumerate}

@@

\subsection{Domain-specific optimization for climate science}

>>>>

The focus of year three in this Ambizione project was the integration of a scalable
polyhedral core infrastructure into real-world compilers (e.g, LLVM/MLIR),
establishing backends for targetting accelerators such as GPUs and FPGAs, and,
finally, developing good performance models. As mentioned in the year 2
report, our focus moved from Julia to MLIR as a compiler and programming
language infrastructure.

@@

\begin{enumerate}
\item Fast, robust, and correct polyhedral libraries
\item Solid polyhedral compiler infrastructure
\begin{itemize}
\item  Modular pattern-based optimizations for CPU and GPU systems
\item 
DeLICM: Scalar dependence removal
\end{itemize}
\item Fast GPU code generation for climate models
\end{enumerate}

@@

\subsection{Fast GPU code generation for climate models}
